\Huge{Vipassana for Hackers} \\ \large{Paper Two: The Brain} \\ \large\textit{Version 0.2}

### 2019-10-06 paper-two/paper-two.tex
paper two including side homunculus

The sensory homunculus which is a part of the somatosensory cortex is a cortical representation
of the body based on the degree of sensory innervation. \cite{sensoryhom}

\todo{Include side image of PSC here.}

>>>>

The Sensory Homunculus which is a part of the Somatosensory Cortex is a cortical representation
of the body based on the degree of sensory innervation. \cite{sensoryhom}

\begin{figure}[H]
  \centering
  \includegraphics[width=5cm]{images/side-somatosensory.png}
  \caption{Location of the Sensory Homunculus.}
  \label{fig:side-somatosensory}
\end{figure}
